[Re] A Generalized Linear Integrate-and-Fire Neural Model Produces Diverse Spiking Behaviors

### 2017-10-04 article/detorakis-2017.tex
markdown file fixed

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Georgios Detorakis,
  },
            pdftitle=
{
[Re] A Generalized Linear Integrate-and-Fire Neural Model Produces Diverse
        Spiking Behavior
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

\usepackage{float,lscape}
\usepackage{xcolor,colortbl}
\usepackage{amssymb,amsmath,array,amsthm}
\usepackage{marvosym}
% \usepackage{makecell}
\usepackage{boldline}
\usepackage{bm,array}

\usepackage{adjustbox}

\newcommand{\Rm}[1]{\mathrm{#1}}

\newcolumntype{C}{>{\centering\arraybackslash}p{3.5em}}

\makeatletter
\newcommand{\thickhline}{%
    \noalign {\ifnum 0=`}\fi \hrule height 1pt
    \futurelet \reserved@a \@xhline
}
\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
\makeatother

\definecolor{Gray}{gray}{0.75}
\definecolor{LightGray}{gray}{0.95}

@@

    \usepackage{authblk}
                        \author[1]{Georgios Detorakis}
                            \affil[1]{Department of Cognitive Sciences, UC Irvine,
                            Irvine, CA, USA}

\date{\vspace{-5mm}
      \sffamily \small
      \href{mailto:corresponding-author@mail.com}{gdetorak@uci.edu \\
      gdetor@protonmail.com}}

@@

  \begin{flushleft}
  {\bfseries Competing Interests:}\\
  The author has declared that no competing interests exist.
  \end{flushleft}

@@

Integrate-and-fire neurons are being used extensively in the field of 
neuroscience for modeling spiking behaviors~\cite{dayan:2001}. In this work we
provide a reference implementation of~\cite{mihalas:2009}, where the authors
have introduced a generalization of the leaky integrate-and-fire neuron model. 
The Mihalas-Niebur Neuron (MNN) model is a linear integrate-and-fire neuron
model capable of expressing a rich spiking behavior based on a set of 
parameters.

An MNN model expresses tonic and phasic spiking, class $1$ and $2$, spike
frequency adaptation, accommodation, threshold variability, rebound spike,
integrator, input bistability, hyperpolarizing spiking and bursting, tonic,
phasic and rebound bursting, mixed mode, afterpotentials, basal bistability, 
preferred frequency and spike latency. 
Due to its simplicity, the MNN model has been used in neuromorphic 
implementations such as~\cite{folowosele:2011}.

The model consists of linear differential equations, which describe the membrane
and threshold potentials and internal currents. All the results provided in 
\cite{mihalas:2009} have been obtained by using only two internal currents and
thus we use the exact same number of internal currents in this work. The
differential equations describe the subthreshold dynamics, while the 
instantaneous threshold potential controls when the neuron firing an action 
potential (spike) in a dynamic way. The ability of the MNN model to generate
such a diverse spiking behavior is due to the complex update rules. In this 
work the MNN model has been implemented in Python (version 3.6.1) using 
Numpy (version 1.13.1) and Matplotlib (version 2.0.2) packages.

@@

In order to implement the model described in \cite{mihalas:2009}, we discretized
the dynamical system using the Euler's integration scheme. The time step is 
fixed to $0.1\, \Rm{ms}$ for all the simulations, and the simulation time
varies according to figure 1 of the original paper. We provide all equations
and parameters of the model in tables as it has been suggested
by~\cite{nordlie:2009}. 
Table~\ref{table:1} provides the summary of the model. Tables~\ref{table:2}
and~\ref{table:3} give the subthreshold dynamics (differential equations) 
describing the membrane and the threshold potentials as well as the two internal
currents and the update rules. The parameters for all the simulations are given
in table~\ref{table:4}. Table~\ref{table:5} provides the external current
intensities (and pulse durations), and initial conditions are described
in table~\ref{table:6}.

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{ll}
        \thickhline
        \multicolumn{2}{c}{Model Summary} \\\thickhline
        \rowcolor{Gray}
        Populations  & No population -- single neuron model \\\rowcolor{LightGray}
        Topology     & -- \\ \rowcolor{Gray}
        Connectivity & -- \\ \rowcolor{LightGray}
        Neuron Model & Linear Integrate-and-Fire Neuron \\\rowcolor{Gray}
        Channel Models & Linear, first order ODEs  \\ \rowcolor{LightGray}
        Synapse Model & -- \\ \rowcolor{Gray}
        Plasticity & -- \\ \rowcolor{LightGray}
        Input & Constant current or rectangular pulses \\\rowcolor{Gray}
        Measurements & Membrane potential, phase plane \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Summary of the model}} 
    \label{table:1}
\end{table}
%%

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{p{3.5cm}ll}
        \thickhline
        \multicolumn{2}{c}{Neuron Model} \\\thickhline
        \rowcolor{Gray}
        Name  &  Mihalas-Niebur Neuron (MNN) \\ \rowcolor{LightGray}
        Type  &  Linear Leaky Integrate-and-Fire Neuron  \\ \rowcolor{Gray}
        Membrane Potential & $
            \begin{aligned}
                \frac{\Rm{d}V(t)}{\Rm{d}t} &= \frac{1}{C} \Big(I_e + I_1 + I_2 - G(V(t) -
                E_L)  \Big)
            \end{aligned}$ \\ \rowcolor{LightGray}
        Instantaneous Threshold Potential  & $
            \begin{aligned}
                \frac{\Rm{d}\Theta(t)}{\Rm{d}t} &= a(V(t) - E_L) - b(\Theta(t) -
                \Theta_{\infty}) 
            \end{aligned} $
            \\ \rowcolor{Gray}
        Internal Currents & $
            \begin{aligned}
                \frac{\Rm{d}I_{1}(t)}{\Rm{d}t} &= -k_1I_1(t)\\
                \frac{\Rm{d}I_{2}(t)}{\Rm{d}t} &= -k_2I_2(t) \\
            \end{aligned} $
    \end{tabular}
    \caption{{\bfseries \sffamily Description of the subthreshold dynamics of
    Mihalas-Niebur neuron model.} $V(t)$ and $\Theta(t)$ are the membrane and 
    threshold potentials, respectively. $E_L$ and $\Theta_{\infty}$ are the
    reversal potentials for the membrane and the threshold variables,
    respectively. $a, b, k_1, k_2$ and $G$ are constant parameters. $I_e$ is
    the external current applied on the neuron model.} 
    \label{table:2}
\end{table}
%%

\begin{table}[!htbp]
    \centering
    \begin{tabular}{cc}
        \thickhline
        \multicolumn{2}{c}{Update rules} \\ \thickhline
        Variable & Rule  \\ \rowcolor{Gray}
        $V(t)$ & $V_r$  \\ \rowcolor{LightGray}
        $\Theta(t)$ & $\max\{\Theta_r, \Theta(t) \}$ \\ \rowcolor{Gray}
        $I_1(t)$ & $R_1 \times I_1(t) + A_1$ \\ \rowcolor{LightGray} 
        $I_2(t) $ & $R_2 \times I_2(t) + A_2$ \\\thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Update rules.} $V_r$ and $\Theta_r$
    are the reset values for the membrane and threshold potentials,
    respectively. $R_1, R_2, A_1$ and $A_2$ are constants.}
    \label{table:3}
\end{table}
%%

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{CCCCC}
        \thickhline
        \multicolumn{5}{c}{Model Parameters} \\\thickhline
           \begin{tabular}[x]{@{}c@{}} Figure \\  \end{tabular}
         & \begin{tabular}[x]{@{}c@{}} $a$ \\ $(\Rm{s^{-1}})$ \end{tabular}
         & \begin{tabular}[x]{@{}c@{}} $A_1/C$ \\ $(\Rm{V/s})$ \end{tabular}
         & \begin{tabular}[x]{@{}c@{}} $A_2/C$ \\ $(\Rm{V/s})$ \end{tabular}& 
           \begin{tabular}[x]{@{}c@{}} $t_f$ \\ $(\Rm{s})$ \end{tabular} \\
        \thickhline
        1A & $0$ & $0$ & $0$ & $0.2$ \\\rowcolor{Gray}
        1B & $0$ & $0$ & $0$ & $0.5$  \\\rowcolor{LightGray}
        1C & $5$ & $0$ & $0$ & $0.2$ \\\rowcolor{Gray}
        1D & $5$ & $0$ & $0$ & $0.5$ \\\rowcolor{LightGray}
        1E & $5$ & $0$ & $0$ & $1.0$ \\\rowcolor{Gray}
        1F & $5$ & $0$ & $0$ & $0.4$ \\\rowcolor{LightGray}
        1G & $5$ & $0$ & $0$ & $1.0$  \\\rowcolor{Gray}
        1H &  $5$ & $0$ & $0$ & $0.3$ \\\rowcolor{LightGray}
        1I & $5$  & $0$ & $0$ & $0.4$ \\\rowcolor{Gray}
        1J & $5$ & $0$ & $0$ & $1.0$ \\\rowcolor{LightGray}
        1K & $30$ & $0$ & $0$ & $0.4$ \\\rowcolor{Gray}
        1L & $30$  & $10$ & $-0.6$ & $0.4$ \\\rowcolor{LightGray}
        1M & $5$ & $10$ & $-0.6$ & $0.5$ \\\rowcolor{Gray}
        1N & $5$ & $10$ & $-0.6$ & $0.5$ \\\rowcolor{LightGray}
        1O & $5$ & $10$ & $-0.6$ & $1.0$ \\\rowcolor{Gray}
        1P & $5$  & $5$ & $-0.3$ & $0.5$ \\\rowcolor{LightGray}
        1Q & $5$  & $5$ & $-0.3$ & $0.2$ \\\rowcolor{Gray}
        1R & $0$ & $8$ & $-0.1$ & $0.2$ \\\rowcolor{LightGray}
        1S & $5$ & $-3$ & $0.5$ & $0.8$ \\\rowcolor{Gray}
        1T &  $-80$ & $0$ & $0$ & $0.05$ \\
        \thickhline
        \multicolumn{5}{l}{Common Parameters} \\\rowcolor{LightGray}
        \thickhline
        \multicolumn{5}{p{22.5em}}{
            $b = 10\, \Rm{s^{-1}}$, $G/C = 50\, \Rm{s^{-1}}$,
            $k_1 = 200\, \Rm{s^{-1}}$, $k_2 = 20\, \Rm{s^{-1}}$,
            $\Theta_{\infty} = -0.05\, \Rm{V}$,
            $R_1 = 0$, $R_2 = 1$, $E_l = -0.07\, \Rm{V}$,
            $V_r = -0.07\, \Rm{V}$, $\Theta_r = -0.06\, \Rm{V}$.
        }
        \\\thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Simulation Parameters}  }
    \label{table:4}
\end{table}
%%

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{CCp{28.2em}}
        \thickhline
        \multicolumn{3}{c}{Model Parameters} \\ \thickhline
        Figure & Type & $I_e/C (\Rm{V/s})$  \\
        \thickhline
        1A & \includegraphics[width=0.1\textwidth]{figs/const.pdf} & $1.5$ \\\rowcolor{Gray}
        1B & \includegraphics[width=0.1\textwidth]{figs/const.pdf} & $1 + 10^{-6}$ \\\rowcolor{LightGray}
        1C & \includegraphics[width=0.1\textwidth]{figs/const.pdf} & $2$ \\\rowcolor{Gray}
        1D &\includegraphics[width=0.1\textwidth]{figs/const.pdf} & $1.5$ \\\rowcolor{LightGray}
        1E &\includegraphics[width=0.1\textwidth]{figs/pulse.pdf} & 
              $1.5 (0.1 \Rm{s}),\, 0 (0.5\Rm{s}),\, 0.5 (0.1\Rm{s}),\, 1
              (0.1\Rm{s}),\, 1.5 (0.1\Rm{s}),\, 0 (0.1 \Rm{s})$
              \\\rowcolor{Gray}
        1F &\includegraphics[width=0.1\textwidth]{figs/pulse.pdf} & $1.5 (0.02
        \Rm{s}),\, 0 (0.18 \Rm{s}),\, -1.5 (0.025 \Rm{s}),\, 0 (0.025
        \Rm{s}),\, 1.5 (0.025 \Rm{s}),\, 0 (0.125 \Rm{s})$
        \\\rowcolor{LightGray} 
        1G & \includegraphics[width=0.1\textwidth]{figs/pulse.pdf} & $0 (0.05
        \Rm{s}),\, -3.5 (0.756 \Rm{s}),\, 0 (0.194 \Rm{s})$ \\\rowcolor{Gray} 
        1H & \includegraphics[width=0.1\textwidth]{figs/const.pdf} & $2(1 +
        10^{-6})$ \\\rowcolor{LightGray}
        1I & \includegraphics[width=0.1\textwidth]{figs/pulse.pdf} & 
        \begin{tabular}[x]{@{}c@{}} 
        $1.5 (0.02 \Rm{s}),\, 0 (0.01 \Rm{s}),\, 1.5 (0.02 \Rm{s}),\,
            0 (0.25 \Rm{s}),\, 1.5 (0.02 \Rm{s}),\, 0 (0.02 \Rm{s}) $\\
            $ 1.5 (0.02 \Rm{s}),\, 0 (0.04 \Rm{s})$ 
        \end{tabular}
            \\\rowcolor{Gray}
        1J & \includegraphics[width=0.1\textwidth]{figs/pulse.pdf} & $1.5 (0.1
        \Rm{s}),\, 1.7 (0.4 \Rm{s}),\, 1.5 (0.1 \Rm{s}),\, 1.7 (0.4 \Rm{s})$
        \\\rowcolor{LightGray}
        1K & \includegraphics[width=0.1\textwidth]{figs/const.pdf} & $-1$  \\\rowcolor{Gray}
        1L & \includegraphics[width=0.1\textwidth]{figs/const.pdf} & $-1$ \\\rowcolor{LightGray}
        1M & \includegraphics[width=0.1\textwidth]{figs/const.pdf} & $2$ \\\rowcolor{Gray}
        1N & \includegraphics[width=0.1\textwidth]{figs/const.pdf} & $1.5$  \\\rowcolor{LightGray}
        1O &\includegraphics[width=0.1\textwidth]{figs/pulse.pdf} & $0 (0.1 
        \Rm{s}),\, -3.5 (0.5 \Rm{s}),\, 0 (0.4 \Rm{s})$ \\\rowcolor{Gray}
        1P & \includegraphics[width=0.1\textwidth]{figs/const.pdf} & $2$ \\\rowcolor{LightGray}
        1Q & \includegraphics[width=0.1\textwidth]{figs/pulse.pdf} & $2 (0.015
        \Rm{s}),\, 0 (0.185 \Rm{s})$  \\\rowcolor{Gray}
        1R & \includegraphics[width=0.1\textwidth]{figs/pulse.pdf}& $5 (0.01
        \Rm{s}),\, 0 (0.09 \Rm{s}),\, 5 (0.01 \Rm{s}),\, 0 (0.09 \Rm{s})$
        \\\rowcolor{LightGray}
        1S & \includegraphics[width=0.1\textwidth]{figs/pulse.pdf}&
        \begin{tabular}[x]{@{}c@{}} 
            $5 (0.005 \Rm{s}),\, 0 (0.005 \Rm{s}),\, 4 (0.005 \Rm{s}),\, 0 (0.385 \Rm{s}),\,
            5 (0.005 \Rm{s}),\, 0 (0.045 \Rm{s}) $\\
            $4 (0.005\Rm{s}),\, 0 (0.345 \Rm{s}) $
        \end{tabular}
        \\\rowcolor{Gray}
        1T & \includegraphics[width=0.1\textwidth]{figs/pulse.pdf} & $8 (0.002 \Rm{s}),\, 0 (0.048 \Rm{s})$ \\
        \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily External current.} This table provides the
    external current for each panel in Figure~\ref{fig:1}. There are two types
    of external currents, constants and pulses. In the case of pulses the
    duration of each pulse is given in seconds along with its intensity.
    }
    \label{table:5}
\end{table}
%%

%%
\begin{table}[!htbp]
    \centering
    \begin{tabular}{cc}
        \thickhline
        \multicolumn{2}{c}{Initial Conditions} \\ \thickhline
        Variable & Initial Value  \\ 
        \rowcolor{Gray}
        $V(t)$ & $-0.07\, \Rm{V}$ / $-0.03\, \Rm{V}$ (Figure 1H) \\ \rowcolor{LightGray}
        $\Theta(t)$ & $-0.05\, \Rm{V}$ / $-0.03\, \Rm{V}$ (Figure 1H) \\ \rowcolor{Gray}
        $I_1(t)$ & $0.01\, \Rm{V}$ \\ \rowcolor{LightGray} 
        $I_2(t) $ & $0.001\, \Rm{V}$ \\ \thickhline
    \end{tabular}
    \caption{{\bfseries \sffamily Initial conditions.} In all simulations
    have been used the same initial conditions, except from the one 
    illustrated in figure~\ref{fig:1}H.}
    \label{table:6}
\end{table}
%%

All simulations ran on a Dell OptiPlex $7040$, equipped with a sixth
generation i$7$ processor, $16\, \Rm{GB}$ of physical memory and running Arch
Linux. The total execution time of all simulations was $2.41$ seconds and the
peak consumed memory was $162\, \Rm{MB}$\footnote{Python memory profiler used
    (\url{https://pypi.python.org/pypi/memory_profiler}).}\@.

\clearpage

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
% \usepackage[utf8]{inputenc}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{hyperref}
\usepackage{amssymb,amsmath,array,amsthm}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor=
{
      Georgios Detorakis,
  },
            pdftitle=
{
[Re] A Generalized Linear Integrate-and-Fire Neural Model Produces Diverse
Spiking Behaviors
},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=blue,
            pdfborder={0 0 0}}
\urlstyle{same}
\usepackage{tcolorbox}
\usepackage{ragged2e}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{caption}
\usepackage{listings}
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}

@@

    \usepackage{authblk}
                        \author[1]{Georgios Detorakis}
                            \affil[1]{Department of Cognitive Sciences, UC Irvine, Irvine CA, USA}

\date{\vspace{-5mm}
      \sffamily \small \href{mailto:gdetorak@uci.edu (gdetor@protonmail.com)}{gdetorak@uci.edu (gdetor@protonmail.com)}}

@@

  \begin{flushleft}
  {\bfseries Competing Interests:}\\
  The authors have declared that no competing interests exist.
  \end{flushleft}

@@

Integrate-and-fire neurons are being used extensively in the field of
neuroscience for modeling spiking behaviors~\autocite{dayan:2001}. In
this work we provide a reference implementation
of~\autocite{mihalas:2009}, where the authors have introduced a
generalization of the leaky integrate-and-fire neuron model. The
Mihalas-Niebur Neuron (MNN) model is a linear integrate-and-fire neuron
model capable of expressing a rich spiking behavior based on a set of
parameters.

An MNN model expresses tonic and phasic spiking, class \(1\) and \(2\),
spike frequency adaptation, accommodation, threshold variability,
rebound spike, integrator, input bistability, hyperpolarizing spiking
and bursting, tonic, phasic and rebound bursting, mixed mode,
afterpotentials, basal bistability, preferred frequency and spike
latency. Due to its simplicity, the MNN model has been used in
neuromorphic implementations such as~\autocite{folowosele:2011}.

The model consists of linear differential equations, which describe the
membrane and threshold potentials and internal currents. All the results
provided in \autocite{mihalas:2009} have been obtained by using only two
internal currents and thus we use the exact same number of internal
currents in this work. The subthreshold dynamics are defined by a set of
linear ordinary differential equations, while an instantaneous threshold
potential controls when the neuron fires an action potential (spike) in
a dynamic way. The ability of the MNN model to generate such a diverse
spiking behavior is due to the complex update rules. In this work the
MNN model has been implemented in Python (version 3.6.1) using Numpy
(version 1.13.1) and Matplotlib (version 2.0.2) packages.

@@

In order to implement the model described in \autocite{mihalas:2009}, we
discretized the dynamical system using the forward Euler integration
scheme. The time step is fixed to \(0.1\, \mathrm{ms}\) for all the
simulations, and the total simulation time \(t_f\) varies according to
figure 1 of the original paper. Our implementation differs from the one
in the original paper, since in \autocite{mihalas:2009}, authors
numerically solve equation \(3.5\) (algebraic equation) under the
constraint imposed by inequality \(3.4\) and thus they compute the spike
times. On the other hand, in this work we directly compute numerically
the solution of the dynamical system defined by equations \(2.1\) and
\(2.2\) in \autocite{mihalas:2009} (see tables~~\ref{tbl:2}
and~~\ref{tbl:3}).

We provide all equations and parameters of the model in tables as it has
been suggested by~\autocite{nordlie:2009}. Table~~\ref{tbl:1} provides
the summary of the model. Tables~~\ref{tbl:2} and~~\ref{tbl:3} give the
subthreshold dynamics (differential equations) describing the membrane
and the threshold potentials as well as the two internal currents and
the update rules. The parameters for all the simulations are given in
table~~\ref{tbl:4}, while the external current intensities and pulse
duration are provided in table~~\ref{tbl:5}. The parameters in this work
are exactly the same used in the original paper (table 1, pg. \(711\)).
We had to infer the time intervals and the total simulation times for
the pulses since they are not given explicitly in the original paper.
Thus, we extracted the time intervals from figure \(1\) of
\autocite{mihalas:2009} by visual inspection. The initial conditions are
given in table~~\ref{tbl:6}.

All simulations ran on a Dell OptiPlex \(7040\), equipped with a sixth
generation i\(7\) processor, \(16\, \mathrm{GB}\) of physical memory and
running Arch Linux (x\(86\_64\)). The total execution time of all
simulations was \(2.41\) seconds and the peak consumed memory was
\(162\, {\mathrm{MB}}\)\footnote{Python memory profiler used
  (\url{https://pypi.python.org/pypi/memory_profiler}).}.

\hypertarget{tbl:1}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl:1}\textbf{Summary of the model.} }\tabularnewline
\toprule
Model Summary &\tabularnewline
\midrule
\endfirsthead
\toprule
Model Summary &\tabularnewline
\midrule
\endhead
Populations & No population -- single neuron model\tabularnewline
Topology & --\tabularnewline
Connectivity & --\tabularnewline
Neuron Model & Linear Integrate-and-Fire Neuron\tabularnewline
Channel Models & Linear, first order ODEs\tabularnewline
Synapse Model & --\tabularnewline
Plasticity & --\tabularnewline
Input & Constant current/rectangular pulses\tabularnewline
Measurements & Membrane potential, phase plane\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{tbl:2}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl:2}Description of the subthreshold dynamics of
Mihalas--Niebur neuron model. \(V(t)\) and \(\Theta(t)\) are the
membrane and threshold potentials, respectively. \(E_L\) and
\(\Theta_{\infty}\) are the reversal potentials for the membrane and
threshold variables, respectively. \(a, b, k_1, k_2\) and \(G\) are
constant parameters. \(I_e\) is the external current applied on the
neuron model. }\tabularnewline
\toprule
Neuron Model &\tabularnewline
\midrule
\endfirsthead
\toprule
Neuron Model &\tabularnewline
\midrule
\endhead
Name & Mihalas-Niebur Neuron (MNN)\tabularnewline
Type & Linear Leaky Integrate-and-Fire Neuron\tabularnewline
Membrane Potential &
\( \frac{\mathrm{d}V(t)}{\mathrm{d}t} = \frac{1}{C} \Big(I_e + I_1 + I_2 - G(V(t) - E_L)  \Big) \)\tabularnewline
Instantaneous Threshold Potential &
\( \frac{\mathrm{d}\Theta(t)}{\mathrm{d}t} = a(V(t) - E_L) - b(\Theta(t) - \Theta_{\infty}) \)\tabularnewline
Internal Currents &
\( \frac{\mathrm{d}I_{1}(t)}{\mathrm{d}t} = -k_1I_1(t) \)\tabularnewline
&
\( \frac{\mathrm{d}I_{2}(t)}{\mathrm{d}t} = -k_2I_2(t) \)\tabularnewline
\bottomrule
\end{longtable}

\pagebreak

\hypertarget{tbl:3}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl:3}\textbf{Update rules.} \(V_r\) and \(\Theta_r\)
are the reset values for the membrane and threshold potentials,
respectively. \(R_1, R_2, A_1\) and \(A_2\) are constants.
}\tabularnewline
\toprule
Variable & Rule\tabularnewline
\midrule
\endfirsthead
\toprule
Variable & Rule\tabularnewline
\midrule
\endhead
\(V(t)\) & \(V_r\)\tabularnewline
\(\Theta(t)\) & \(\max\{\Theta_r, \Theta(t) \}\)\tabularnewline
\(I_1(t)\) & \(R_1 \times I_1(t) + A_1\)\tabularnewline
\(I_2(t)\) & \(R_2 \times I_2(t) + A_2\)\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{tbl:4}{}
\begin{longtable}[]{@{}lllll@{}}
\caption{\label{tbl:4}\textbf{Simulation Parameters}. Common parameters
for all simulations: \(b = 10\, \mathrm{s^{-1}}\),
\(G/C = 50\, \mathrm{s^{-1}}\), \(k_1 = 200\, \mathrm{s^{-1}}\),
\(k_2 = 20\, \mathrm{s^{-1}}\),
\(\Theta_{\infty} = -0.05\, \mathrm{V}\), \(R_1 = 0\), \(R_2 = 1\),
\(E_l = -0.07\, \mathrm{V}\), \(V_r = -0.07\, \mathrm{V}\),
\(\Theta_r = -0.06\, \mathrm{V}\). }\tabularnewline
\toprule
Figure & \(a (\mathrm{s^{-1}})\) & \(\frac{A_1}{C} (\mathrm{V/s})\) &
\(\frac{A_2}{C} (\mathrm{V/s})\) & \(t_f \mathrm{s}\)\tabularnewline
\midrule
\endfirsthead
\toprule
Figure & \(a (\mathrm{s^{-1}})\) & \(\frac{A_1}{C} (\mathrm{V/s})\) &
\(\frac{A_2}{C} (\mathrm{V/s})\) & \(t_f \mathrm{s}\)\tabularnewline
\midrule
\endhead
1A & \(0\) & \(0\) & \(0\) & \(0.2\)\tabularnewline
1B & \(0\) & \(0\) & \(0\) & \(0.5\)\tabularnewline
1C & \(5\) & \(0\) & \(0\) & \(0.2\)\tabularnewline
1D & \(5\) & \(0\) & \(0\) & \(0.5\)\tabularnewline
1E & \(5\) & \(0\) & \(0\) & \(1.0\)\tabularnewline
1F & \(5\) & \(0\) & \(0\) & \(0.4\)\tabularnewline
1G & \(5\) & \(0\) & \(0\) & \(1.0\)\tabularnewline
1H & \(5\) & \(0\) & \(0\) & \(0.3\)\tabularnewline
1I & \(5\) & \(0\) & \(0\) & \(0.4\)\tabularnewline
1J & \(5\) & \(0\) & \(0\) & \(1.0\)\tabularnewline
1K & \(30\) & \(0\) & \(0\) & \(0.4\)\tabularnewline
1L & \(30\) & \(10\) & \(-0.6\) & \(0.4\)\tabularnewline
1M & \(5\) & \(10\) & \(-0.6\) & \(0.5\)\tabularnewline
1N & \(5\) & \(10\) & \(-0.6\) & \(0.5\)\tabularnewline
1O & \(5\) & \(10\) & \(-0.6\) & \(1.0\)\tabularnewline
1P & \(5\) & \(5\) & \(-0.3\) & \(0.5\)\tabularnewline
1Q & \(5\) & \(5\) & \(-0.3\) & \(0.2\)\tabularnewline
1R & \(0\) & \(8\) & \(-0.1\) & \(0.2\)\tabularnewline
1S & \(5\) & \(-3\) & \(0.5\) & \(0.8\)\tabularnewline
1T & \(-80\) & \(0\) & \(0\) & \(0.05\)\tabularnewline
\bottomrule
\end{longtable}

\pagebreak

\hypertarget{tbl:5}{}
\begin{longtable}[]{@{}lll@{}}
\caption{\label{tbl:5}\textbf{External current}. This table provides the
external current for each panel in Figure~~\ref{fig:1}. There are two
types of external currents, constants and pulses. In the case of pulses
the duration of each pulse is given in seconds along with its intensity.
}\tabularnewline
\toprule
Figure & Type & \(I_e/C (V/s)\)\tabularnewline
\midrule
\endfirsthead
\toprule
Figure & Type & \(I_e/C (V/s)\)\tabularnewline
\midrule
\endhead
1A & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(1.5\)\tabularnewline
1B & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(1 + 10^{-6}\)\tabularnewline
1C & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(2\)\tabularnewline
1D & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(1.5\)\tabularnewline
1E & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(1.5 (0.1 \mathrm{s}),\, 0 (0.5\mathrm{s}),\, 0.5 (0.1\mathrm{s}),\, 1 (0.1\mathrm{s}),\, 1.5 (0.1\mathrm{s}),\, 0 (0.1 \mathrm{s}) \)\tabularnewline
1F & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(1.5 (0.02 \mathrm{s}),\, 0 (0.18 \mathrm{s}),\, -1.5 (0.025 \mathrm{s}),\, 0 (0.025 \mathrm{s}),\, 1.5 (0.025 \mathrm{s}),\, 0 (0.125 \mathrm{s})\)\tabularnewline
1G & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(0 (0.05 \mathrm{s}),\, -3.5 (0.756 \mathrm{s}),\, 0 (0.194 \mathrm{s}) \)\tabularnewline
1H & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\( 2(1 + 10^{-6}) \)\tabularnewline
1I & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\( 1.5 (0.02 \mathrm{s}),\, 0 (0.01 \mathrm{s}),\, 1.5 (0.02 \mathrm{s}),\, 0 (0.25 \mathrm{s}),\, 1.5 (0.02 \mathrm{s}),\, 0 (0.02 \mathrm{s})\)\tabularnewline
& & \( 1.5 (0.02 \mathrm{s}),\, 0 (0.04 \mathrm{s}) \)\tabularnewline
1J & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\( 1.5 (0.1 \mathrm{s}),\, 1.7 (0.4 \mathrm{s}),\, 1.5 (0.1 \mathrm{s}),\, 1.7 (0.4 \mathrm{s}) \)\tabularnewline
1K & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(-1\)\tabularnewline
1L & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(-1\)\tabularnewline
1M & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(2\)\tabularnewline
1N & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(1.5\)\tabularnewline
1O & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(0 (0.1 \mathrm{s}),\, -3.5 (0.5 \mathrm{s}),\, 0 (0.4 \mathrm{s})\)\tabularnewline
1P & \includegraphics[width=0.10000\textwidth]{figs/const.pdf} &
\(2\)\tabularnewline
1Q & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(2 (0.015 \mathrm{s}),\, 0 (0.185 \mathrm{s})\)\tabularnewline
1R & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(5 (0.01 \mathrm{s}),\, 0 (0.09 \mathrm{s}),\, 5 (0.01 \mathrm{s}),\, 0 (0.09 \mathrm{s})\)\tabularnewline
1S & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(5 (0.005 \mathrm{s}),\, 0 (0.005 \mathrm{s}),\, 4 (0.005 \mathrm{s}),\, 0 (0.385 \mathrm{s}),\, 5 (0.005 \mathrm{s}),\, 0 (0.045 \mathrm{s}) \)\tabularnewline
& & \(4 (0.005\mathrm{s}),\, 0 (0.345 \mathrm{s}) \)\tabularnewline
1T & \includegraphics[width=0.10000\textwidth]{figs/pulse.pdf} &
\(8 (0.002 {\mathrm{s}}),\, 0 (0.048 \mathrm{s})\)\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{tbl:6}{}
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tbl:6}\textbf{Initial Conditions} In all simulations the
same initial conditions have been used, except from the one illustrated
in Figure ~\ref{fig:1} H. }\tabularnewline
\toprule
Variable & Initial Value\tabularnewline
\midrule
\endfirsthead
\toprule
Variable & Initial Value\tabularnewline
\midrule
\endhead
\(V(t)\) & \(-0.07\, \mathrm{V}\) / \(-0.03\, \mathrm{V}\) (Figure
1H)\tabularnewline
\(\Theta(t)\) & \(-0.05\, \mathrm{V}\) / \(-0.03\, \mathrm{V}\) (Figure
1H)\tabularnewline
\(I_1(t)\) & \(0.01\, \mathrm{V}\)\tabularnewline
\(I_2(t)\) & \(0.001\, \mathrm{V}\)\tabularnewline
\bottomrule
\end{longtable}
